Automated verification of stand-alone solar photovoltaic systems

### 2018-11-21 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
We have evaluated five case studies in total. Related to the results of the automated verification and the evaluation if the results are correct: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during automated verification, but there was found flaws related with the battery autonomy, when SOC reached a empty-battery level. The automated verification identified the flaws (for all houses) right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this flaw at house 1; 611.2 hours to house 2; 615.8 hours to house 3, and 620.8 hours to house 4. This possible flaws were confirmed with the dwellers that owns the systems by interview: at least once a mouth is usual the system to turn off, normally in raining or clouds days, reaching the situation described in Step 3 of \ref{table:controller}; and after the sun rises, the systems returns to normal operation.

>>>>

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system, it was identified that, in fact, the system most of the time does not meet the battery autonomy (mainly when all the loads are turned on). That behavior is expected since the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but we have found flaws related to the battery autonomy, when SOC reached a empty-battery level. Our verification engine identified the flaws (for all houses) right after the first night-discharge cycle, before the solar system started to recharge the batteries. Our verification engine took 409.3 hours to find this flaw in house 1; 611.2 hours to house 2; 615.8 hours to house 3, and 620.8 hours to house 4. This possible flaws were confirmed with the dwellers that owns the systems by interview: at least once a mouth is usual the system to turn off, normally in raining or clouds days, reaching the situation described in Step 3 of~\ref{table:controller}; and after the sun rises, the systems returns to normal operation.
